Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-31 demystify.tex
updates

Some schools send out admission letters in batches, some do rolling admission, and some do not send anything out (e.g., you're on their waitlist, or they might not send rejection letters).  In general, you should hear back from most schools by around March (but some schools might take longer!).

In short, you should not worry too much about the timeline. Also do not send emails asking about interviews or status (unless you have interviewed specifically with someone then you can ask that person for status updates and others \autoref{sec:accept-postpone-decline}).

@@

>>>>

Some schools send out admission letters in batches, some do rolling admission, and some do not send anything out (e.g., you're on their waitlist, or they might not send rejection letters).  In general, you should hear back from most schools by mid-March (but some schools might take longer!).

In short, there is not much you can do about this other than to be patient and wait. Also do not send emails asking about interviews or status (unless you have interviewed specifically with someone then you can ask that person for status updates and others \autoref{sec:accept-postpone-decline}).

@@

%\section{Why are rejection letters sent so late?}\label{sec:late-rejection}

%"Just reject me already!" is a common sentiment among applicants.  Indeed, school will first send out admission offers to the top candidates. They do not send out rejection letters because there is still a chance that some of the top candidates will decline the offer. If they do, then the school will go to the next set of candidates and send out offers to them.  This process continues until all spots are filled.  This is why you might not hear back until late in the admission cycle.
